Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-05-19 tex/old/test-WW-type-00t-PS.tex
last version

\definecolor{darkgreen}{rgb}{0,0.65,0}
\newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
\newcommand{\PS}[1]{\blue{\bf\boldmath #1}}

@@

\author[a]{S.~Bastami}
\author[c]{H.~Avakian}
\author[d]{A.~V.~Efremov} 
\author[e,f]{A.~Kotzinian} 
\author[g]{B.~U.~Musch} 
\author[e]{B.~Parsamyan} 
\author[b,c]{A.~Prokudin} 
\author[i]{M.~Schlegel} 
\author[]{G.~Schnell} 
\author[a,i]{P.~Schweitzer} 
\author[i]{W.~Vogelsang}

\affiliation[a]{Department of Physics, University of Connecticut, 
	Storrs, CT 06269, U.S.A.}
\affiliation[b]{Division of Science, Penn State Berks, Reading, 
	PA 19610, USA}
\affiliation[c]{Thomas Jefferson National Accelerator Facility, 
	Newport News, VA 23606, U.S.A.}
\affiliation[d]{Joint Institute for Nuclear Research, Dubna, 
	141980 Russia}
\affiliation[e]{Yerevan Physics Institute,
2 Alikhanyan Brothers St.,
375036 Yerevan, Armenia
}
\affiliation[f]{INFN, Sezione di Torino, 10125 Torino, Italy
}

\affiliation[g]{Institut f\"ur Theoretische Physik, Universit\"at 
  	Regensburg, 93040 Regensburg, Germany}
\affiliation[i]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
	% Auf der Morgenstelle 14, 
	D-72076 T\"ubingen, Germany}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{saman.bastami@uconn.edu}
%\emailAdd{mda5232@psu.edu} % Mason Dale Albright
\emailAdd{avakian@jlab.org}
\emailAdd{efremov@theor.jinr.ru}
\emailAdd{aram.kotzinian@cern.ch}
\emailAdd{bmusch@b-mu.de}
\emailAdd{bakur@cern.ch}
\emailAdd{prokudin@jlab.org}
\emailAdd{marc.schlegel@uni-tuebingen.de}
\emailAdd{peter.schweitzer@phys.uconn.edu}
\emailAdd{werner.vogelsang@uni-tuebingen.de}

%\date{\today}
%===================  PREPRINT NUMBER, JOURNAL =======================
%\
%===================  ABSTRACT =======================================
%\begin{abstract}
\abstract{ 
We present the complete cross-section for pion production in Semi-Inclusive 
Deep Inelastic Scattering (SIDIS) in the Wandzura-Wilczek-type approximation 
up to power-suppressed ${\cal O}(1/Q^2)$ terms. We compute all % 18 
twist-2 and twist-3 SIDIS structure functions and the corresponding 
asymmetries. We discuss  the applicability of the
Wandzura-Wilczek-type approximations on the basis of available data,
and make predictions which can be tested by data from 
Jefferson Lab, COMPASS, HERMES, and the future EIC. 
The results of this paper can be readily used for phenomenology and 
for event generators for SIDIS, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura-Wilczek approximation, 
	semi-inclusive deep inelastic scattering, 
	transverse momentum dependent distribution functions, 
	spin and azimuthal asymmetries, leading and subleading twist}

@@

A great deal of what is known about the quark-gluon structure of 
nucleon is due to studies of parton distribution functions (PDFs) 
in deeply inelastic reactions. Leading-twist PDFs  tell us  how likely 
it is to find an unpolarized parton 
(described by PDF $f_1^a(x)$, $a=q,\,\bar q,\,g$) 
or a longitudinally polarized parton 
(described by PDF $g_1^a(x)$, $a=q,\,\bar q,\,g$)
in a fast-moving unpolarized or longitudinally polarized nucleon, 
which carries the fraction $x$ of the nucleon momentum.
This information depends on the ``resolution (renormalization) scale'' 
associated with the hard scale $Q$ of the process.
%, which we will not indicate for notational simplicity.
Although the PDFs  $f_1^a(x)$ and $g_1^a(x)$ continue being the 
subject of intense research (small-$x$, large-$x$, helicity sea 
and gluon distributions) they can be considered as rather 
well-known, and the frontier has been extended in the last years 
to go beyond the one-dimensional picture offered by PDFs.

One way to do this consists in a systematic inclusion of transverse 
parton momenta $\kperp$ whose effects manifest themselves in terms of
transverse momenta of the reaction products in the final state.
If these transverse momenta are much smaller than the hard scale $Q$
of the process, the formal description is given in terms of 
transverse momentum dependent distribution functions (TMDs) 
and fragmentation functions (FFs)
which are defined in terms of quark-quark correlators 
\cite{Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
and depend on two independent variables: the fraction $x$ of 
nucleon momentum carried by parton, and intrinsic transverse 
momentum $\kperp$ of the parton.
Being a vector in the plane transverse with respect to the
light-cone direction singled out by the hard momentum flow in the process,
$\kperp$ allows us to access novel information on the nucleon spin structure 
through correlations of $\kperp$ with nucleon and/or parton spin. The 
latter is a well-defined concept for twist-2 TMDs interpreted in 
the infinite momentum frame or in lightcone quantization formalism.

One powerful tool to study TMDs are measurements of the SIDIS process.
By exploring various possibilities for electron/muon beam and target 
polarizations unambiguous information can be accessed on the 8 leading-twist 
TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
linear combinations of the 16 subleading-twist TMDs 
\cite{Goeke:2005hb,Bacchetta:2006tn}.
Complementary information can be obtained 
from the Drell-Yan process \cite{Arnold:2008kf}, 
and $e^+e^-$ annihilation \cite{Metz:2016swz}.

@@

The striking observation is that the $\bar qgq$-terms in $g_T^a(x)$ 
and $h_L^a(x)$ are small: theoretical mechanisms predict this 
\cite{Balla:1997hf,Dressler:1999hc,Gockeler:2000ja,Gockeler:2005vw}, 
and in the case of $g_T^a(x)$ data confirm or are compatible with these 
predictions \cite{Abe:1998wq,Anthony:2002hy}.
This approximation (``neglect of $\bar qgq$-terms'') is commonly 
known as Wandzura-Wilczek (WW) approximation \cite{Wandzura:1977qf}.
The possibility to apply this type of approximation also to TMDs has 
been explored in specific cases in \cite{Kotzinian:1995cz,Kotzinian:1997wt,
Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk}.
In both cases, PDFs and TMDs, one basically assumes that the 
contributions from $\bar{q}gq$-terms can be neglected with respect to 
$\bar{q}q$-terms. But the nature of the omitted matrix elements is 
different, and in the context of TMDs one often prefers to speak 
about WW-type approximations.

In this work, after introducing the SIDIS process and defining TMDs and FFs 
(Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the approximations,
and review what is presently known about their reliability from experiment 
and theory (Sec.~\ref{Sec-3:WW}).
We will show that under the assumption of the validity of these approximations 
it is possible to describe all leading and subleading SIDIS structure functions
in terms of a basis of 6 TMDs and 2 FFs, and review what is presently known
about these functions (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}).
Using the latest available extractions of the 8 basis functions  
we will systematically apply the WW and/or WW-type approximations
to SIDIS structure at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist.
We will conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).

This is the first study of all SIDIS structure functions up to twist-3 
in a unique approach. Our results are of use for experiments prepared 
in the near-term (Jefferson Lab 12) or proposed in the long-term 
(Electron Ion Collider), and provide helpful input for Montecarlo event
generators \cite{Avakian:2015vha}.
Our predictions will either be confirmed within the expected accuracy, 
implying the approximations work and calling for dedicated theoretical 
explanations why. Or they will fail in certain cases, calling for 
theoretical work to explain why in some cases $\bar{q}gq$-terms are sizable.
In any case, our results will deepen our understanding.

@@

%------ BEGIN FIGURE 1: Kinematics of SIDIS ---------------------------
\begin{wrapfigure}[8]{RD}{8cm}
\vspace{-5mm}
\centering
	\includegraphics[width=7.5cm]{\FigPath/Fig02a-kin-SIDIS-UT.eps}
        \caption{\label{fig-kin-SIDIS}
    	Kinematics of SIDIS process $lN\to l^\prime h X$.} 
	% and the definitions of azimuthal angles in the lab frame.}
\vspace{-5mm}
\end{wrapfigure}
%------ END FIGURE 1 -------------------------------------------------

The SIDIS process is sketched in 
Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
electron and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
from which azimuthal angles are counted. The relevant kinematic invariants 
are
\ba
   x  = \frac{Q^2}{2\,P\cdot  q}, \;\;
   y = \frac{P \cdot  q}{P \cdot  l}, \;\;
   z = \frac{P \cdot  P_h}{P\cdot  q}, \;\;
%   \gamma = \frac{2 M x}{Q} \; .
   Q^2=-q^2.
\label{eq:xyz}\;\;\;\;\ea
In addition to $x$, $y$, $z$ the cross section is also differential 
in the azimuthal angle $\phi_h$ of the produced hadron, the square 
of its momentum component $\Phperp$ perpendicular with respect to the 
virtual photon momentum, and the azimuthal angle $\psi_l$ characterizing 
the overall orientation of the lepton scattering plane in the lab frame.
Notice that $d \psi_l \simeq d\phi_S$ where $\phi_S$ is the azimuthal angle
of the nucleon spin vector. It is convenient to define the unpolarized
lepton -- quark scattering cross section
\ba\label{Eq:sigma0-FUU}
	\sigma_0 \equiv \frac{d \sigma}{dy} 
	= 
	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
	\biggl(1-y+\frac12y^2\biggr)\;
\ea

To leading order in $1/Q$ the SIDIS cross-section is given by  
\begin{subequations}\ba\hspace{-1cm}
   &&  \frac{d^6\sigma_{\rm leading}}{dx\,dy\,dz\,d\phi_S\,d\phi_h\,d \Phperp^2}
   =	 \frac{\sigma_0 }{4\pi}\; F_{UU}(x,z,\Phperp^2)
        \Biggl\{\;1 
        + \cos(2\phi_h)\,   p_1\,A_{UU}^{\cos(2\phi_h)} \nonumber\\
   && \hspace{2cm}
  	+ S_L\sin(2\phi_h)\,p_1\,A_{UL}^{\sin(2\phi_h)}    
	+ \lambda\,S_L\,    p_2\,A_{LL}  \phantom{\frac11}\nonumber\\
   && \hspace{2cm}
	+ \lambda\,S_T\cos(\phi_h-\phi_S)\,p_2\,A_{LT}^{\cos( \phi_h-\phi_S)}
       	+ S_T\sin( \phi_h-\phi_S)\, A_{UT}^{\sin( \phi_h-\phi_S)} \phantom{\frac11}
	\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin( \phi_h+\phi_S)\,p_1\,A_{UT}^{\sin( \phi_h+\phi_S)} 
        + S_T\sin(3\phi_h-\phi_S)\,p_1\,A_{UT}^{\sin(3\phi_h-\phi_S)}\Biggr\}
    \hspace{1cm} \label{Eq:SIDIS-leading}
\ea
where $F_{UU}$ is the structure function due to transverse
polarization of the virtual photon (sometimes denoted as $F_{UU,T}$),
and we systematically neglect $1/Q^2$ corrections in 
kinematic factors and a structure function arising from
longitudinal polarization of the virtual photon 
(sometimes denoted as $F_{UU,L}$). %  poorly known in SIDIS.
The structure functions (and asymmetries $A$) also depend on $Q^2$ via the scale dependence of 
TMDs and FFs, which we do not show in formulas throughout this work.

At subleading order one has
\ba\hspace{-1cm}
   &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\phi_S\,d\phi_h\,d \Phperp^2}
   =	\frac{\sigma_0 }{4\pi} \; F_{UU}(x,z,\Phperp^2)
        \Biggl\{ 
          \cos(\phi_h)\,p_3\,A_{UU}^{\cos(\phi_h)}
  	{}
	\nonumber\\ 
   && \hspace{2cm}
	+ \lambda\sin(\phi_h)\,p_4\,A_{LU}^{\sin(\phi_h)}+ S_L\sin(\phi_h)\,p_3\,A_{UL}^{\sin(\phi_h)}    
	+ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} \phantom{\frac11}\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin(2\phi_h-\phi_S)\,p_3\,A_{UT}^{\sin(2\phi_h-\phi_S)}
        + \lambda\,S_L\cos(\phi_h)\,p_4\,A_{LL}^{\cos(\phi_h)}\phantom{\frac11}
	\nonumber\\
   && \hspace{2cm}
  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
        + \lambda\,S_T\cos(2\phi_h-\phi_S)\,p_4\,A_{LT}^{\cos(2\phi_h-\phi_S)}
	\Biggr\}
   \hspace{1cm} \label{Eq:SIDIS-subleading}
\ea\end{subequations}
Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by 
% \ba\label{Eq:y-prefactors}
% &&	p_1 = \varepsilon \equiv  
%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2} 
%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
% &&	p_2 = \sqrt{1-\epsilon^2} \approx
%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
% \ea
\be\label{Eq:y-prefactors}
	p_1 = \frac{1-y}{1-y+\frac12\,y^2} 		\, , \;\;\;
	p_2 = \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2}	\, , \;\;\;
	p_3 = \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2} 	\, , \;\;\;
	p_4 = \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2}     	\, .
\ee
and the asymmetries are defined as 
\be
	A_{XY}^{\rm weight}\equiv A_{XY}^{\rm weight}(x,z,\Phperp)=
	\frac{F_{XY}^{\rm weight}(x,z,\Phperp)}{F_{UU}(x,z,\Phperp)}.
\ee
Hereby the first index $X=U(L)$ denotes the unpolarized beam
(longitudinally polarized beam with helicity $\lambda$).
The second index $Y=U(L,T)$ refers to the target which can be unpolarized
(or longitudinally, transversely polarized with respect to virtual photon).
The superscript ``weight'' indicates the azimuthal dependence with no index 
indicating an isotropic angular distribution of the produced hadrons.

>>>>

\definecolor{darkgreen}{rgb}{0,0.65,0}
\newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
\newcommand{\ps}[1]{\blue{ #1}}

@@

\author[a]{S.~Bastami}
\author[b]{H.~Avakian}
\author[c]{A.~V.~Efremov} 
\author[d,e]{A.~Kotzinian} 
\author[f]{B.~U.~Musch} 
\author[e]{B.~Parsamyan} 
\author[g,b]{A.~Prokudin} 
\author[h]{M.~Schlegel} 
\author[i]{G.~Schnell} 
\author[a,j]{P.~Schweitzer} 
\author[a]{K.~Tezgin}
\author[j]{W.~Vogelsang}

\affiliation[a]{Department of Physics, University of Connecticut, 
	Storrs, CT 06269, U.S.A.}
\affiliation[b]{Thomas Jefferson National Accelerator Facility, 
	Newport News, VA 23606, U.S.A.}
\affiliation[c]{Joint Institute for Nuclear Research, Dubna, 
	141980 Russia}
\affiliation[d]{Yerevan Physics Institute,  Alikhanyan Brothers St.,
	375036 Yerevan, Armenia}
\affiliation[e]{INFN, Sezione di Torino, 
	10125 Torino, Italy}
\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
  	Regensburg, 93040 Regensburg, Germany}
\affiliation[g]{Division of Science, Penn State Berks, Reading, 
	PA 19610, USA}
\affiliation[h]{Department of Physics, New Mexico State University, 
	Las Cruces, NM 88003-001, USA}
\affiliation[i]{Department of Theoretical Physics, University of the Basque 
	Country UPV/EHU, 48080 Bilbao, Spain, and
	IKERBASQUE, Basque Foundation for Science, 48013 Bilbao, Spain}
\affiliation[j]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
	D-72076 T\"ubingen, Germany} % Auf der Morgenstelle 14,

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{saman.bastami@uconn.edu}
\emailAdd{avakian@jlab.org}
\emailAdd{efremov@theor.jinr.ru}
\emailAdd{aram.kotzinian@cern.ch}
\emailAdd{bmusch@b-mu.de}
\emailAdd{bakur@cern.ch}
\emailAdd{prokudin@jlab.org}
\emailAdd{schlegel@nmsu.edu}
\emailAdd{gunar.schnell@desy.de}
\emailAdd{peter.schweitzer@phys.uconn.edu}
\emailAdd{kemal.tezgin@uconn.edu}
\emailAdd{werner.vogelsang@uni-tuebingen.de}

%\date{\today}
%===================  PREPRINT NUMBER, JOURNAL =======================
%\
%===================  ABSTRACT =======================================
%\begin{abstract}
\abstract{ 
We present the complete cross-section for pion production in semi-inclusive 
deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in 
the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
neglect of $q\bar q g$-terms with respect to $\bar{q}q$-correlators.}
We compute all twist-2 and twist-3 structure functions and the corresponding 
asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
approximations on the basis of available data. We make predictions which 
can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
Electron-Ion Collider. The results of this paper can be readily used for 
phenomenology and for event generators, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura--Wilczek approximation, 
	semi-inclusive deep inelastic scattering, 
	transverse momentum dependent distribution functions, 
	spin and azimuthal asymmetries, leading and subleading twist}

@@

A great deal of what is known about the quark-gluon structure of 
nucleon is due to studies of parton distribution functions (PDFs) 
in deep-inelastic reactions. leading--twist PDFs  tell us  how likely 
it is to find an unpolarized parton 
(described by PDF $f_1^a(x)$, $a=q,\,\bar q,\,g$) 
or a longitudinally polarized parton 
(described by PDF $g_1^a(x)$, $a=q,\,\bar q,\,g$)
in a fast-moving unpolarized or longitudinally polarized nucleon, 
which carries the fraction $x$ of the nucleon momentum.
This information depends on the ``resolution (renormalization) scale'' 
associated with the hard scale $Q$ of the process.
%, which we will not indicate for notational simplicity.
Although the PDFs  $f_1^a(x)$ and $g_1^a(x)$ continue being the 
subject of intense research (small-$x$, large-$x$, helicity sea 
and gluon distributions) they can be considered as rather 
well-known, and the frontier has been extended in the last years 
to go beyond the one-dimensional picture offered by those PDFs.

One way to do this consists in a systematic inclusion of transverse 
parton momenta $\kperp$ whose effects manifest themselves in terms of
transverse momenta of the reaction products in the final state.
If these transverse momenta are much smaller than the hard scale $Q$
of the process, the formal description is given in terms of 
transverse momentum dependent distribution functions TMDs) 
and fragmentation functions (FFs)
which are defined in terms of quark-quark correlators 
\cite{Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
and depend on two independent variables: the fraction $x$ of 
nucleon momentum carried by parton, and intrinsic transverse 
momentum $\kperp$ of the parton.
Being a vector in the plane transverse with respect to the
light-cone direction singled out by the hard momentum flow in the process,
$\kperp$ allows us to access novel information on the nucleon spin structure 
through correlations of $\kperp$ with nucleon and/or parton spin. The 
latter is a well-defined concept for twist-2 TMDs interpreted in 
the infinite momentum frame or in lightcone quantization formalism.

One powerful tool to study TMDs are measurements of the 
semi-inclusive deep-inelastic scattering (SIDIS) process.
By exploring various possibilities for electron/muon beam and target 
polarizations unambiguous information can be accessed on the 8 leading--twist 
TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
linear combinations of the 16 subleading--twist TMDs 
\cite{Goeke:2005hb,Bacchetta:2006tn}.
Complementary information can be obtained 
from the Drell-Yan process \cite{Arnold:2008kf}, 
and $e^+e^-$ annihilation \cite{Metz:2016swz}.

@@

The striking observation is that the $\bar qgq$-terms in $g_T^a(x)$ 
and $h_L^a(x)$ are small: theoretical mechanisms predict this 
\cite{Balla:1997hf,Dressler:1999hc,Gockeler:2000ja,Gockeler:2005vw}, 
and in the case of $g_T^a(x)$ data confirm or are compatible with these 
predictions \cite{Abe:1998wq,Anthony:2002hy,Airapetian:2011wu}.
This approximation (``neglect of $\bar qgq$-terms'') is commonly 
known as Wandzura--Wilczek (WW) approximation \cite{Wandzura:1977qf}.
The possibility to apply this type of approximation also to TMDs has 
been explored in specific cases in \cite{Kotzinian:1995cz,Kotzinian:1997wt,
Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk,Tangerman:1994bb}.
In both cases, PDFs and TMDs, one basically assumes that the 
contributions from $\bar{q}gq$-terms can be neglected with respect to 
$\bar{q}q$-terms. But the nature of the omitted matrix elements is 
different, and in the context of TMDs one often prefers to speak 
about WW-type approximations.

In this work, after introducing the SIDIS process and defining TMDs and FFs 
(Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type) 
approximations, and review what is presently known about them 
from experiment and theory (Sec.~\ref{Sec-3:WW}).
We will show that under the assumption of the validity of these approximations 
all leading and subleading SIDIS structure functions are described in terms of 
a basis of 6 TMDs and 2 FFs (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}),
and review how these basis functions describe available data 
(Sec.~\ref{Sec-5:twist-2+basis}).
We will systematically apply the WW and/or WW-type approximations
to SIDIS structure at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist, and
conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).

This is the first study of all SIDIS structure functions up to twist-3 
in a unique approach. Our results are of importance for experiments prepared 
in the near-term (JLab 12, \ps{COMPASS}) or proposed in the long-term 
(Electron Ion Collider), and provide helpful input for Monte Carlo event
generators \cite{Avakian:2015vha}.
Our predictions will either be confirmed within the expected accuracy
\ps{or not be supported by data. The first case will call for dedicated 
theoretical studies to explain why the pertinent $\bar{q}gq$-terms are 
so small. The second case will call for explanations why sometimes 
$\bar{q}gq$-terms are so sizable. In this way our work will help to guide 
further developments. In either case our results will deepen the
understanding of the quark-gluon correlations inside hadrons.}

@@

%------ BEGIN FIGURE 1: Kinematics of SIDIS ---------------------------
\begin{wrapfigure}[8]{RD}{8cm}
\vspace{-7mm}
\centering
	\includegraphics[width=7.2cm]{\FigPath/Fig02a-kin-SIDIS-UT.eps}
        \caption{\label{fig-kin-SIDIS}
    	Kinematics of SIDIS process $lN\to l^\prime h X$
	in 1-photon exchange approximation.}
\vspace{-5mm}
\end{wrapfigure}
%------ END FIGURE 1 -------------------------------------------------

The SIDIS process is sketched in 
Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
electron and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
from which azimuthal angles are counted. The relevant kinematic invariants 
are
\ba
   x  = \frac{Q^2}{2\,P\cdot  q}, \;\;
   y = \frac{P \cdot  q}{P \cdot  l}, \;\;
   z = \frac{P \cdot  P_h}{P\cdot  q}, \;\;
%   \gamma = \frac{2 M x}{Q} \; .
   Q^2=-q^2.
\label{eq:xyz}\;\;\;\;\ea
In addition to $x$, $y$, $z$ the cross section is also differential 
in the azimuthal angle $\phi_h$ of the produced hadron, the square 
of its momentum component $\Phperp$ perpendicular with respect to the 
virtual photon momentum. 
\ps{In principle the cross section is also differential with respect to the} 
azimuthal angle $\psi_l$ characterizing the overall orientation of the 
lepton scattering plane in \ps{a fixed} lab frame.
%
% Notice that $d \psi_l \simeq d\phi_S$ where $\phi_S$ is the azimuthal angle
% of the nucleon spin vector. 
%
\ps{By analyzing the data in the reference frame in Fig.~\ref{fig-kin-SIDIS}
all events are by definition in the ``bin'' $\psi_l=0$ (within detector
resolution) and the variable $\psi_l$ is practically integrated out leaving 
us with a 5-dimensional cross section. Below we keep the cross section 
``differential'' in $\psi_l$ for symbolic reasons.}
%
It is convenient to define the unpolarized
lepton--quark scattering \ps{subprocess} cross section
\ba\label{Eq:sigma0-FUU}
	% \sigma_0 \equiv 
	\frac{d \hat{\sigma}}{dy} 
	= 
	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
	\biggl(1-y+\frac12y^2\biggr)\;
\ea

To leading order in $1/Q$ the SIDIS cross-section is given by  
\begin{subequations}\ba\hspace{-1cm}
   &&  \frac{d^6\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
   =	 \frac{1}{4\pi}\;\frac{d \hat{\sigma}}{dy}\;F_{UU}(x,z,\Phperp^2)
        \Biggl\{\;1 
        + \cos(2\phi_h)\,   p_1\,A_{UU}^{\cos(2\phi_h)} \nonumber\\
   && \hspace{2cm}
  	+ S_L\sin(2\phi_h)\,p_1\,A_{UL}^{\sin(2\phi_h)}    
	+ \lambda\,S_L\,    p_2\,A_{LL}  \phantom{\frac11}\nonumber\\
   && \hspace{2cm}
	+ \lambda\,S_T\cos(\phi_h-\phi_S)\,p_2\,A_{LT}^{\cos( \phi_h-\phi_S)}
       	+ S_T\sin( \phi_h-\phi_S)\, A_{UT}^{\sin( \phi_h-\phi_S)} \phantom{\frac11}
	\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin( \phi_h+\phi_S)\,p_1\,A_{UT}^{\sin( \phi_h+\phi_S)} 
        + S_T\sin(3\phi_h-\phi_S)\,p_1\,A_{UT}^{\sin(3\phi_h-\phi_S)}\Biggr\}
    \hspace{1cm} \label{Eq:SIDIS-leading}
\ea
where $F_{UU}$ is the structure function due to transverse
polarization of the virtual photon (sometimes denoted as $F_{UU,T}$),
and we systematically neglect $1/Q^2$ corrections in kinematic factors 
and a structure function (sometimes denoted as $F_{UU,L}$) arising from
longitudinal polarization of the virtual photon (and analog for the 
structure function $\propto S_T\,\sin( \phi_h-\phi_S)$, see below).
The structure functions 
(and asymmetries) also depend on $Q^2$ via the scale dependence of 
TMDs and FFs, which we do not show in formulas throughout this work.

At subleading order \ps{in the $1/Q$ expansion} one has
\ba\hspace{-1cm}
   &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
   =	\frac{1}{4\pi} \; \frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z,\Phperp^2)
        \Biggl\{ 
          \cos(\phi_h)\,p_3\,A_{UU}^{\cos(\phi_h)}
	\nonumber\\ 
   && \hspace{2cm}
	+ \lambda\sin(\phi_h)\,p_4\,A_{LU}^{\sin(\phi_h)}+ S_L\sin(\phi_h)\,p_3\,A_{UL}^{\sin(\phi_h)}    
	+ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} \phantom{\frac11}\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin(2\phi_h-\phi_S)\,p_3\,A_{UT}^{\sin(2\phi_h-\phi_S)}
        + \lambda\,S_L\cos(\phi_h)\,p_4\,A_{LL}^{\cos(\phi_h)}\phantom{\frac11}
	\nonumber\\
   && \hspace{2cm}
  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
        + \lambda\,S_T\cos(2\phi_h-\phi_S)\,p_4\,A_{LT}^{\cos(2\phi_h-\phi_S)}
	\Biggr\}
   \hspace{1cm} \label{Eq:SIDIS-subleading}
\ea\end{subequations}
Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by 
% \ba\label{Eq:y-prefactors}
% &&	p_1 = \varepsilon \equiv  
%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2} 
%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
% &&	p_2 = \sqrt{1-\epsilon^2} \approx
%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
% \ea
\be\label{Eq:y-prefactors}
	p_1 = \frac{1-y}{1-y+\frac12\,y^2} 		\, , \;\;\;
	p_2 = \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2}	\, , \;\;\;
	p_3 = \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2} 	\, , \;\;\;
	p_4 = \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2}     	\, .
\ee
and the asymmetries are defined as 
\be
	A_{XY}^{\rm weight}\equiv A_{XY}^{\rm weight}(x,z,\Phperp)=
	\frac{F_{XY}^{\rm weight}(x,z,\Phperp)}{F_{UU}(x,z,\Phperp)}.
\ee
Hereby the first index $X=U(L)$ denotes the unpolarized beam
(longitudinally polarized beam with helicity $\lambda$).
The second index $Y=U(L,T)$ refers to the target which can be unpolarized
(or longitudinally, transversely polarized with respect to virtual photon).
The superscript ``weight'' indicates the azimuthal dependence with no index 
indicating an isotropic angular distribution of the produced hadrons.

\ps{In the partonic description the structure functions in 
(\ref{Eq:SIDIS-leading})    are ``twist-2.'' Those in
(\ref{Eq:SIDIS-subleading}) are ``twist-3'' and contain a
factor $M/Q$ in their definitions, see below. In our treatment to $1/Q^2$ 
accuracy we neglect two structure functions due to longitudinal virtual 
photon polarization which contribute at order ${\cal O}(M^2/Q^2)$ in the 
partonic description of the process, one being $F_{UU,L}$ and the other 
contributing to the $\sin(\phi_h-\phi_S)$ angular distribution 
\cite{Bacchetta:2006tn}.}
